---
title: "Group_Project_Markdown"
output: html_document
---

**Variable description**

The following table will present the variables in the final datamart and a description of each of these:

Variable Name  | Description
-------------  | -------------
UserID         | User ID was of each participant at time of registration assigned by bwin
total_conv_amount   | The sum of poker chip transaction amount per User ID
avg_conv_amount   | The average of poker chip transaction amount per User ID
total_sell_amount   |The total amount sold per User ID
total_buy_amount   | The total amount bought per User ID
avg_timediff_hours   | The average time difference between conversions
nr_conversions   | The number of poker chip transactions per User ID
RegistrationDate   | Date of registration of each participant
Age   | Participant's age
FOTotalStakes   | Total stakes each participant betted on fixed-odds plays from February 1, 2005 through September 30, 2005
FOTotalWinnings   | Total winnings each participant received on fixed-odds plays from February 1, 2005 through September 30, 2005
FOTotalBets   | Total number of bets each participant betted on fixed-odds plays from February 1, 2005 through September 30, 2005
FOFirstActiveDate   | First date of fixed-odds play of each participant from February 1, 2005 through September 30, 2005
FOLastActiveDate   | Last date of fixed-odds play of each participant from February 1, 2005 through September 30, 2005
FOTotalDaysActive   | Total days of active fixed-odds plays of each participant from February 1, 2005 through September 30, 2005
LATotalStakes   | Total stakes each participant betted on live-action plays from February 1, 2005 through September 30, 2005
LATotalWinnings   | Total winnings each participant received on live-action plays from February 1, 2005 through September 30, 2005
LATotalBets   | Total number of bets each participant betted on live-action plays from February 1, 2005 through September 30, 2005
LAFirstActiveDate   | First date of live-action play of each participant from February 1, 2005 through September 30, 2005
LALastActiveDate   | Last date of live-action play of each participant from February 1, 2005 through September 30, 2005
LATotalDaysActive   | Total days of active live-action plays of each participant from February 1, 2005 through September 30, 2005
FirstSportsActiveDate   | First date of active sports book play for each participant from February 1, 2005 through September 30, 2005
RegDate   | Date of registration
FirstPay   | Participant’s first betting money deposits date
FirstAct   | Participant’s first active play date
First_time_sports   | Participant’s first sports book play date
First_time_casino   | Participant’s first casino play date
First_time_games   | Participant’s first games play date
First_time_poker   | Participant’s first poker play date
ApplicationID   | Different route of access to bwin (ID)
avg_bet   | Average number of daily bets per participant
min_bet   | Minimum number of bets made by a participant
max_bet   | Maximum number of bets made by a participant
total_number_bets   | Total number of bets the participant has made
avg_winnings   | Average betting winnings per participant
min_winnings   | Minimum betting winnings per participant
max_winnings   | Maximum betting winnings per participant
total_money_bets   |Total betting stakes per participant, in €
min_money_bets   | Minimum betting stakes per participant, in €
max_money_bets   | Maximum betting stakes per participant ,in €
mean_money_bets   | Average betting stakes per participant ,in €
Betted_Casino_boss   | Number of bets the participant made for this product category
Betted_Casino_chartwell   | Number of bets the participant made for this product category
Betted_Games_bwin   | Number of bets the participant made for this product category
Betted_Games_VS   | Number of bets the participant made for this product category
Betted_Sports_fixed_live   | Number of bets the participant made for this product category
Betted_Sports_fixed_odd   |Number of bets the participant made for this product category
Betted_Supertoto   | Number of bets the participant made for this product category
Gender   | Participant's Gender (1: Female; 0: Male)
Language   | Participant's language code
Country   | Participant's country of residence code
country_name   | Participant's country of residence name
country   | Participant's country of residence abbreviation
latitude   | Participant's country of residence latitude
longitude   | Participant's country of residence longitude
Continent_Name   | Participant's country of residence continent name
Continent_Code   | Participant's country of residence continent code
application_description   | Name of the different routes of access to bwin
TotalDaysActive   | Number of days each participant was active
gender_description   | Participant's gender
LastActiveDate   | Last date each participant was active


# Demographics charts

**Gender chart**

As the following graph shows, there are 39060 Male participants against 3588 Female participant, which are about 92% Male being active on Internet sports Betting. 

```{r}
# Gender Donut Chart
library(readr)
library(dplyr)
library(ggplot2)
datamart <- read_csv("C:/Users/fceli/Desktop/BIG DATA/7. Business Analytics Tools - Open Source/Group Assignment/Final files/R_Group_Assignment/datamart.csv")
gender1 <- datamart%>% 
  filter(is.na(gender_description)==FALSE) %>%
  group_by(gender_description) %>% 
  summarise(count_gender=n())
# Add addition columns, needed for drawing with geom_rect.
gender1$fraction = gender1$count_gender / sum(gender1$count_gender)
gender1 = gender1[order(gender1$fraction), ]
gender1$ymax = cumsum(gender1$fraction)
gender1$ymin = c(0, head(gender1$ymax, n=-1))
ggplot(gender1, aes(fill=gender_description, ymax=ymax, ymin=ymin, xmax=4, xmin=3)) +
     geom_rect(colour="grey30") +
     coord_polar(theta="y") +
     xlim(c(0, 4)) +
     theme_bw() +
     theme(panel.grid=element_blank()) +
     theme(axis.text=element_blank()) +
     theme(axis.ticks=element_blank()) +
     labs(title="Gender")
```


**Number of users per country**

The following graph represents the top 15 countries in terms of number of participants. Germany is by far the most represented country with 24000 users, followed by Turkey, Poland, Spain, Greece, France and Denmark. 
```{r}
#Country Chart
clients <- datamart%>% 
  group_by(country_name) %>% 
  summarise(count_people=n())%>%
  arrange(desc(count_people))%>%
  slice(1:15)
clients<-na.omit(clients)
ggplot(clients, aes(x=reorder(country_name, -count_people), y=count_people, label=count_people)) + 
  geom_bar(stat = "identity")+
  scale_fill_manual("legend", values = "Blue")+#c("A" = "black", "B" = "orange", "C" = "blue"))+
  geom_text(size=1, position=position_stack(vjust=0.5))+
  theme(axis.text.x=element_text(angle=90, hjust=1))+
  labs(title= "Number of users per country")
```

